---
title: "Untitled"
author: "Cameron Sims"
date: "6/9/2021"
output: html_document
---

```{r setup, include=FALSE}
# Display options
knitr::opts_chunk$set(echo = TRUE)

# Load necessary libraries
library("dplyr")
library("ggplot2")

# Source my_rf_cv function
source("../Code/my_rf_cv.R")

# Source data
my_penguins <- read.csv("../Data/my_penguins.csv")
```

In this analysis, I will use my_penguins.csv data to predict mody_mass_g using
covariates bill_length_mm, bill_depth_mm, and flipper_length_mm. I will use
fold sizes of 2, 5, and 10 and run 30 iterations with each size. I will then
make 3 boxplots of the data, a table displaying the average CV estimate and the
standard deviation of the CV estimates for each fold size, and discuss the
observed results. The figures and results will be saved in respectively-named
folders within the "Output" subfolder.

```{r}
# Vector to hold CV estimates MSEs
mses <- c()

# Using k = c(2, 5, 10), perform random forest 30 times each
for (k in c(2, 5, 10)) {
  for (i in 1:30) {
    mses <- append(mses, my_rf_cv(k))
  }
}

# Save MSEs as 30 row, 3 column csv
write.csv(data.frame(k_1 = mses[1:30], k_5 = mses[31:60], k_10 = mses[61:90]),
                     "../Output/Results/simulation_results.csv")

# Separate MSEs by k for boxplot
dat <- data.frame(mse = mses, k = rep(c(2, 5, 10), each = 30))
```

```{r}
# Create a boxplot for each value of k
chart <- ggplot(data = dat, mapping = ggplot2::aes(x = as.factor(k), y = mse)) + 
  geom_boxplot() +
  labs(title = "Distribution Of MSE For Different Numbers Of Folds") +
  xlab("Number of Folds") +
  ylab("CV-Estimated MSE")

# Save chart in "figures" sub-subfolder
ggsave("mse_boxplot.pdf", chart, path = "../Output/Figures")

# Calculate average CV estimate and standard deviation for k = 2
two_avg <- mean(subset(dat, k == 2)$mse)
two_sd <- sd(subset(dat, k == 2)$mse)

# Calculate average CV estimate and standard deviation for k == 5
five_avg <- mean(subset(dat, k == 5)$mse)
five_sd <- sd(subset(dat, k == 5)$mse)

# Calculate average CV estimate and standard deviation for k == 10
ten_avg <- mean(subset(dat, k == 10)$mse)
ten_sd <- sd(subset(dat, k == 10)$mse)

# Save average CV estimates and standard deviations in a table
summary_stats <- data.frame(Mean_CV = c(two_avg, five_avg, ten_avg),
           SD_CV = c(two_sd, five_sd, ten_sd))

# Save summary statistics in "results" sub-subfolder
saveRDS(summary_stats, file = "../Output/Results/summary_stats.rds")
```

From the boxplots, it appears the median CV-Estimated MSE decreases as the
number of folds increases. 5 folds has the smallest interquartile range of
the three fold amounts and exists almost entirely within the range of the
10-fold boxplot. The 2-fold boxplot has the largest range and is centered 
higher than the other boxplots. Numerically, the table shows 10 folds has
the lowest average CV estimate whereas five folds has the lowest CV standard
deviation. Two folds has both the highest mean CV estimate and the highest
CV standard deviation.

Generally, test error (CV MSE) will decrease as the number of folds increases.
This is because more data is being used to calculate the predicted value(s).
However, after a certain point, this value can decrease as the model becomes
less reliable (training error increases). As such, it is possible the best
number of folds is close to five, or between five and ten. While ten folds
might have the lowest mean CV-Estimated MSE, it has higher standard deviation
than five-folds and thus is not conclusively better. 

